Template Master's Thesis

### 2023-08-18 paper.tex
Update analysis

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
	\caption{Time-of-day activity histogram and KDE for a specific ENS address pair}
	\label{fig:ToD}
\end{figure}

@@

Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers. We treat addresses as nodes and add undirected edges between them if they interact with each other. \newline
To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component. The resulting network graph includes 51,566 nodes and 249,302 edges. As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library. \newline
Subsequently, we run ten independent experiments for each method. Our choice of input parameters is identical to \cite{Beres2020}. Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions. \newline
For any node within the embedding, we can easily order all other nodes by the Euclidean distance. We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors. \newline 
This enables us to search for our ENS ground truth pairs and report their relative rank. The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}. Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.

@@

To implement the LAND transfer heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses. Next, we gather all token and native asset transfers associated with the selected transaction hashes. We group the data by transaction hash and examine each transaction's sender (from) and recipient (to) address. If the same user address appears as the sender and recipient, we mark the transaction as a purchase. Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.

@@

@@

LAND transfers between Decentraland addresses can also be visualized as a token network graph. Figure \ref{fig:LAND_network} presents the resulting graph. In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase. Notably, the big cluster previously mentioned is visible on the top-right of the largest connected component. \newline
A few key observations can be made from this network graph. First, most LAND transfers involve some form of compensation, in line with expectations. Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network. Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address. %This could reflect a common strategy among participants in the LAND market.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

@@

%The results chapter or section simply and objectively reports what you found, without speculating on why you found these results. The discussion interprets the meaning of the results, puts them in context, and explains why they matter.
%Discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
%Discussion section: (a) Try to explain "What do your results mean?", and (b) how they relate to the literature,
%DISCUSSION provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.

Discuss which approach worked best for clustering a predefined address set and why.

Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful.

Vergleichen mit \cite{wu2022tutela} und \cite{Beres2020}

The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address

Limitations
%A reference implementation for clustering a predefined address set using node embeddings on Github

Assentiar consuetae ha opinionum mentemque ob ii. Ne conflantur de intelligat et me cohibendam. Imaginandi ob to at agnoscerem et mutationum. In methodum ob ii at quicquid lectorum. Procuravi ha dependent ob evidenter tangantur concipere. Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum. Typis patet prius qua nia mem ens. Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum. Tes illum mundo vetus signa fit talem res his.

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
	\caption{Time-of-day activity histogram and KDE for a selected ENS address pair}
	\label{fig:ToD}
\end{figure}

@@

Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers. We treat addresses as nodes and add undirected edges between them if they interact with each other. \newline
To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component. The resulting network graph includes 51,566 nodes and 249,302 edges. As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library. \newline
Subsequently, we run ten independent experiments for each method. Our choice of input parameters is identical to \cite{Beres2020}. Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions. \newline
For any node within the embedding, we can easily order all other nodes by the Euclidean distance. We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline 
This enables us to search for our ENS ground truth pairs and report their relative rank. The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}. Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.

@@

To implement this clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses. Next, we gather all token and native asset transfers associated with the selected transaction hashes. We group the data by transaction hash and examine each transfer's sender (from) and recipient (to) address. If the same user address appears as the sender and recipient, we mark the transaction as a purchase. Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.

@@

LAND transfers between Decentraland addresses can also be visualized as a token network graph. Figure \ref{fig:LAND_network} presents the resulting graph. In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase. Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component. \newline
A few key observations can be made from this network graph. First, most LAND transfers involve some form of compensation, in line with expectations. Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network. Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address. %This could reflect a common strategy among participants in the LAND market.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_network.png}
	\caption{LAND token network}
	\label{fig:LAND_network}
\end{figure}

\newpage

@@

%The results chapter or section simply and objectively reports what you found, without speculating on why you found these results.

%The discussion
%... interprets the meaning of the results, puts them in context, and explains why they matter.
%... is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
%... Try to explain "What do your results mean?", and how they relate to the literature,
%... provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.

Throughout our analysis, we successfully applied three clustering heuristics to our address set, utilizing the available on-chain data. These heuristics were self-authorization, node embedding, and LAND transfers. In the following discussion, we will examine each of these approaches step-by-step.

%%%%%%%%%%%%%%%%%%%%
Self-authorization is a straightforward technique, but results in very few identified address clusters. This is because it requires a highly specific on-chain behavior, which is rarely observed in practice. In particular, approvals are seldom used to authorize another externally owned account one might own. We also encountered a significant number of false-positives due to non-standard implementations. After excluding these instances, we identified a total of 15 entities consisting of 35 addresses. This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses. In his analysis of transaction data up to Ethereum block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
%%%%%%%%%%%%%%%%%%%%

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. \newline
Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum.

The main reasons for this are the different clustering objectives of previous implementations. \cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of Beres et al. and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with Beres's findings, which identified Diff2Vec as the best method. \newline
However, determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method. % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand.

Wir haben eine eigene Methode entwickelt zum Clustern von Network embeddings.
Wir bauen Clusters abhängig von Euclidischer distanz zwischen feature vectors von nodes. 
Dazu benutzen wir die embeddings von role2vec.
Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl. sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden. Könnte aber auch sein dass wir es falsch angewendet haben.

%und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.
%Im Gegensatz zu früheren implementierungen haben wir intra-set asset transfers benutzt um den graph zu bilden. das ist so weil bei unser spezifischen aufgabe ein vordefiniertes grosses addressen set zu clustern dies besser gelingt als bspw. alle transaktionen im ethereum netzwerk anzuschauen wie tutela oder wie beres der einfach alle token transfers der withdrawal und deposit addressen von tornado cash anschaut, wo sie eher weniger interaktionen haben als bei uns.
%Node embeddings mussten wir an unsere Gegebenheiten anpassen. Evaluierung mittels unsern ENS address paaren, hat gezeigt dass diese methode sehr gut funktioniert um ähnliche addressen zu finden.
%Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. 
%Schwierig zu sagen wieso der eine Appraoch besser ist als der andere, der unterschied zwischen r2v und den anderen zwei ist das r2v ein role-based algorithmus ist und dies für unser spezielles datenset und unsere ENS address pairs besser zu funktionieren scheint. Aber nicht sehr aussagekräftig da kleines sample und alle approaches recht gut.
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
-Eine weitere Methode basierend auf spezifischen on-chain Event vorgeschlagen.
-The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
-lässt sich gut visualisieren und evtl. auch nachvollziehen
-eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar. hat auch funktioniert aber wieder relativ wenige clusters gefunden, hat es falsch positive dabei? zb. offchain zahlungen und on-chain token transferiert
%%%%%%%%%%%%%%%%%%%%%

-Discuss which approach worked best for clustering a predefined address set and why. 
Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.

other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
